%-------------------------------------------------------------------------------
%	SECTION TITLE
%-----------------------------------------------------------------------------
\vspace{-3mm}
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\vspace{-1mm}
\begin{cventries}

%---------------------------------------------------------
\cventry
{\textbf{Core Competencies \& Accomplishments}} % Job title
{\href{https://www.zluri.com/}{Zluri, Bangalore}} % Organization
{Apr. 2022 - Present} % Date(s)
{} % Location
{\begin{cvitems} % Description(s) of tasks/responsibilities
    \item {\textbf{Document Intelligence (NLP):} Architected an end-to-end contract extraction pipeline using \textbf{TensorFlow Transform} and \textbf{Keras} to build a custom Transformer-based NER model. This system automatically identifies renewal dates and fiscal obligations in unstructured PDFs, reducing manual audit time by \textbf{70\%}.}
    \item {\textbf{Predictive Spend Analytics:} Developed a multivariate \textbf{Long Short-Term Memory (LSTM)} network in TensorFlow to forecast SaaS expenditure. By integrating headcount growth and historical billing cycles, the model achieved a \textbf{94\% Mean Absolute Percentage Error (MAPE)}, allowing the Finance team to optimize cash flow.}
    \item {\textbf{Intelligent License Optimization:} Engineered a \textbf{Wide \& Deep learning model} using the \textbf{tf.estimator} API to predict user "churn" from specific SaaS tools. This enabled proactive license reclamation, saving the organization over \textbf{\$400k in annual recurring costs}.}
    \item {\textbf{Shadow IT Detection:} Implemented an anomaly detection system using \textbf{Autoencoders} in TensorFlow to monitor SSO logs and API traffic. This identifies anomalous app-to-app data transfers, uncovering unauthorized "Shadow IT" with a \textbf{45\% higher detection rate} than rule-based systems.}
    \item {\textbf{Recommendation Systems:} Built a \textbf{TensorFlow Recommenders (TFRS)} engine to suggest optimal software tiers for departments. By analyzing usage patterns across the organization, the system increased internal software utility scores by \textbf{30\%}.}
    \item {\textbf{Scalable MLOps with TFX:} Orchestrated the production ML lifecycle using \textbf{TensorFlow Extended (TFX)}.Implemented automated data validation and model analysis, reducing the time-to-production for new feature sets from three weeks to four days.}
    \item {\textbf{Distributed Training \& Performance:} Leveraged \textbf{tf.distribute.MirroredStrategy} to train large-scale classification models on multi-GPU clusters, processing over \textbf{500M+ data points} from global financial feeds and usage logs.}
\end{cvitems}}
%---------------------------------------------------------

%---------------------------------------------------------

%---------------------------------------------------------

%---------------------------------------------------------

%---------------------------------------------------------
\end{cventries}